---
title: "Rmd  file for Q7"
author: "Qurat-ul-Ain Azim"
date: "2022-09-30"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## My Pancake Recipe

### Ingredients

-   1 cup flour

-   1 cup milk

-   1 egg

-   2 tsp baking powder

-   2 pinches of salt

-   2 tbsp oil or melted butter

-   2 tbsp sugar

### Method

Mix all dry ingredients and then add in all wet. This will yield 1.5 cups of batter Mix again. Spoon fourth cup fulls on a heated non-stick pan. Flip when bubbles apper. Cook on the other side for a minute. Take off the pan and enjoy

```{r measurements}
batter_quantity <- function(n_batches) {
  return(n_batches * 1.5)
}
batter_quantity(3)
```

## Measuring Flour

The best way to measure flour for pancakes and cakes is to sccop out using cups and then level with a knife. ! cup of flour should equal 120 grams on scale. Below, we convert flour from cups to grams.

```{r}
cup_to_gram <- function(cups) {
  return(cups * 120)
}
cup_to_gram(5)
```

